---
title: "hw5"
author: "YuaoYang"
date: "2019/11/10"
output: github_document
---


# Problem 1
```{r}

library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r}
fill_miss = function(x) {
  if(is.numeric(x)){
    x = replace_na(x, round(mean(x, na.rm = TRUE),2))
  }else if(is.character(x)){
    x = replace_na(x, "virginica")
  }
}

new_iris = map(iris_with_missing, fill_miss) %>%
  data.frame()


```

#Problem 2

```{r}

file_name = list.files(path = "./data/",full.names = TRUE) 
 
read_data = purrr::map(file_name, read.csv) %>%
  bind_rows() %>%
  mutate(subject_id = str_sub(file_name,8,13),
         arm = ifelse(str_detect(subject_id, "con"),"control_arm", "experimental_arm")) %>%
  select(subject_id, arm, week_1:week_8) %>%
  pivot_longer(cols = 3:10, names_to = "week",names_prefix = "week_",values_to = "value") %>%
  mutate(arm = factor(arm, levels = c("control_arm", "experimental_arm")))

```

```{r}
read_data %>%
  group_by(week) %>%
ggplot(aes(x = week, y = value, group = subject_id, color = subject_id))+
  geom_line() + labs(title = "spaghetti plot of each observation over time") +
   facet_grid(. ~ arm)

```
From the plot, i find the abservational value in experimental arm group are bigger than it in control arm group in overall trend.

#Problem 3

```{r}
set.seed(2)
sim_regression = function(n = 30, beta0 = 2, beta1, variance = 50) {

   sim_data = tibble(

    x = rnorm(n),

    y = beta0 + beta1 * x + rnorm(n, 0,  sqrt (variance)))

  ls_fit = broom::tidy (lm(y ~ x, data = sim_data))
}


result_1  = rerun(10000, sim_regression(beta1 = 0)) %>% 
  bind_rows() %>% 
  filter(term == "x") %>%
  select(estimate, p.value)

result_2  = 
  tibble(beta1 = 1:6) %>% 
  mutate(beta1_new = map(.x = beta1, ~rerun(10000,sim_regression(beta1 =.x)))) %>% 
  unnest()


```

```{r}
sim_result = result_2 %>%
  unnest()

sim_result %>%
 filter(term == "x") %>%
  select(beta1, estimate, p.value) %>%
  filter(p.value< 0.05) %>%
  group_by(beta1) %>%
  summarize(propotion = n()/10000)%>%
  ggplot(aes(x= beta1, y = propotion)) + geom_histogram(stat = "identity")+
   scale_x_continuous(
    breaks = c(1,2,3,4,5,6)) +
  labs(y = "propotion of rejecting the null",
       title ="the plot of propotion of times the null was rejected")
```
From the plot, we can easily find that when beta1 increases, the reject propotion will increase, which means that there is positive relation between effect size and power.
```{r}
total = sim_result %>%
 filter(term == "x") %>%
  select(beta1, estimate, p.value) %>%
  group_by(beta1) %>%
  summarize(mean_beta1 = mean(estimate)) %>%
  mutate(group = "total")
  
  ggplot(total, aes(x= beta1, y = mean_beta1)) + geom_point()+ geom_line()+
   scale_x_continuous(
    breaks = c(1,2,3,4,5,6)) + labs(y = "average estimate of beta1",
                                    x = "true value of beta1",
       title ="the plot of relation between estimate and true beta1")



reject_null = sim_result %>%
 filter(term == "x") %>%
  select(beta1, estimate, p.value) %>%
  filter(p.value< 0.05) %>%
  group_by(beta1) %>%
  summarize(mean_beta1 = mean(estimate)) %>%
  mutate(group = "reject")

  ggplot(reject_null, aes(x= beta1, y = mean_beta1)) + geom_point()+geom_line() +
   scale_x_continuous(
    breaks = c(1,2,3,4,5,6)) +
  labs(y = "average estimate of beta1",
        x = "true value of beta1",
       title ="the plot of relation between estimate and true beta1")

rbind(reject_null,total) %>%
   ggplot(aes(x= beta1, y = mean_beta1, color= group)) + geom_point()+geom_line() +
   scale_x_continuous(
    breaks = c(1,2,3,4,5,6)) +
  labs(y = "average estimate of beta1",
        x = "true value of beta1",
       title ="the plot of relation between estimate and true beta1")
```

From the plot, we can find that the sample average of beta1 is not equal to  true value of beta1.  And the with the effect size increases, the average value will closer to true value. To explain it, we need to return the last propotion plot, according to what I said before, the power is very low when effect size is small, which means there are fewer estimate of beta1 in low effect size and the sample size of estimate is too small to get the accurate average value.